### 2017-09-07 paper/related.tex
pass on related work

\textit{Test Selection:} Research has focused mostly on test suite
minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  \Fix{...} Most of these
techniques are unsound (\ie{}, they do not guarantee that
fault-revealing tests will be selected), however, more recently, sound
techniques have been
proposed~\cite{gligoric-etal-issta2015,soetens-etal-2016}. Recent work
for test selection introduced
Ekstazi~\cite{ekstazi-web,gligoric-etal-issta2015} that conservatively
computes which tests have been impacted by file changes.  A test is
discarded for execution if it does not depend on any changed file
dynamically reachable from execution. Although Ekstazi is focused on
regression test selection, it highlights the importance of parallelism
as a complement to test selection.  In fact, as in their evaluation,
we also discovered subjects with parallelism enabled by default.  Test
suite parallelization is complementary to regression testing
techniques.

%% \textit{Usage of massively parallel hardware:}
\textit{Hardware level parallelization:} Previous research
investigated the feasibility of testing embedded software on Graphics
Processing Units (GPUs) as an alternative to multicore
CPUs~\cite{rajan-etal-ase2014}.  The Simple Instruction Multiple Data
(SIMD) architecture of modern GPUs allows running the same test case
with different test data over several threads.  Although benchmarks
indicate far superior performance over traditional multicore CPUs,
there are severe limitations. Control-flow branching in source code
can impact performance negatively while violating the lock-step
execution during the divergence of instructions~\cite{rajan-etal-ase2017}
%% existing GPU programming-models (\eg{}, CUDA~\cite{cuda}, and
%% OpenCL~\cite{opencl}) are compatible only with a subset of the C/C++
%% language.
Recent work proposed a compiler-assisted approach to make
programs compatible with the relying programming
model~\cite{yaneva-etal-issta2017}.

@@

\textit{Cloud based build tools:}

>>>>

\textit{Test Selection:} Research has focused mostly on test suite
minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  \Fix{...} Most of these
techniques are unsoud (\ie{}, they do not guarantee that
fault-revealing tests will be selected), however, more recently, sound
techniques have been
proposed~\cite{gligoric-etal-issta2015,soetens-etal-2016}. Recent work
for test selection introduced
Ekstazi~\cite{ekstazi-web,gligoric-etal-issta2015} that conservatively
computes which tests have been impacted by file changes.  A test is
discarded for execution if it does not depend on any changed file
dynamically reachable from execution. Although Ekstazi is focused on
regression test selection, it highlights the importance of parallelism
as a complement to test selection.  In fact, as in their evaluation,
we also discovered subjects with parallelism enabled by default.  Test
suite parallelization is complementary to regression testing
techniques.

%% \textit{Usage of massively parallel hardware:}
\textit{Hardware level parallelization:} Previous research
investigated the feasibility of testing embedded software on Graphics
Processing Units (GPUs) as an alternative to multicore
CPUs~\cite{rajan-etal-ase2014}.  The Simple Instruction Multiple Data
(SIMD) architecture of modern GPUs allows running the same test case
with different test data over several threads.  Although benchmarks
indicate far superior performance over traditional multicore CPUs,
there are severe limitations. Control-flow branching in source code
can impact performance negatively while violating the lock-step
execution during the divergence of instructions~\cite{rajan-etal-ase2014}
%% existing GPU programming-models (\eg{}, CUDA~\cite{cuda}, and
%% OpenCL~\cite{opencl}) are compatible only with a subset of the C/C++
%% language.
Recent work proposed a compiler-assisted approach to make programs
compatible with the relying programming-model used by
GPUs to parallelize tests~\cite{yaneva-etal-issta2017}.

@@

\textit{Continuous integration services:}
Recent work showed us that Continuous Integration Services are widely
used and improve the productivity~\Fix{ref ref ref}.
